### 2022-05-26 sections/conferences-full.tex
Update conferences-full.tex

\begin{benumerate}{68}

@@

\item{\small González-Bustamante, B. (2022). {\itshape Resignation Calls and Dismissals of Ministers in Latin America: ata Gathering using NLP and Machine Learning}. Presentation delivered at the XXXIX International Congress of the Latin American Studies Association, Virtual.}\vspace{1mm}

@@

%% Bamberg

>>>>

\begin{benumerate}{69}

@@

\item{\small González-Bustamante, B. (2022). {\itshape Resignation Calls and Dismissals of Ministers in Latin America: Data Gathering using NLP and Machine Learning}. Presentation delivered at the XXXIX International Congress of the Latin American Studies Association, Virtual.}\vspace{1mm}

@@

\item{\small Fleming, T. G., González-Bustamante, B., \& Schleiter, P. (2021). {\itshape Cabinet Reshuffles and Parliamentary No-Confidence Motions}. Presentation delivered at the Otto-Friedrich-Universität Bamberg Workshop, Virtual.}\vspace{1mm}
